---
output:
  html_document:
    code_download: true
    theme: cerulean
    toc: yes
    toc_depth:  3
    toc_float:
      collapsed:  yes
      smooth_scroll: yes
    number_sections: yes
    code_folding:  show

params:
    ORG: "ActBlue"
    TAG: "2022"

title : "`r paste('Summarize .fec files for', ORG, 'in', TAG, 'Election Cycle')`"
author: "Earl F Glynn<br><small>watchdoglab.substack.com</small>"
date  : "<small>`r Sys.Date()`</small>"
---

```{r setup, echo = FALSE}
# http://biostat.mc.vanderbilt.edu/wiki/Main/KnitrHtmlTemplate
require(Hmisc)    # provides knitrSet and other functions
knitrSet(lang = 'markdown',   # If using blogdown: knitrSet(lang='blogdown')
         fig.align = 'left',
         w = 6.5,
         h = 4.5,
         cache = FALSE)
```

`r hidingTOC(buttonLabel = "Outline")`

```{r setup2, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment    = NA)

time.1 <- Sys.time()
```

Notes:

* Review FEC filings of interest, e.g., [ActBlue FEC filings](https://docquery.fec.gov/cgi-bin/forms/C00401224/)

# Setup {.tabset .tabset-fade .tabset-pills}

##  {.active}

## Constants

```{r}
EXCEL_LIMIT <- 2^20
```

```{r}
ORG <- params$ORG
TAG <- params$TAG
```

```{r}
FEC_FILE_DIR <- paste0("K:/Data-Farm/", ORG, "/")

TARGET_DIR   <- paste0(FEC_FILE_DIR, TAG, "/")

Summary_DIR  <- paste0(TARGET_DIR, "FEC-File-Summaries/")

DELIMITER <- "\t"    # tab delimiter
```

### SA Header

For now, use `SA` headers slightly modified from `v8.4 e-filing headers .xlsx`

See `C:\efg-Data-Farm-Scripts\FEC\FEC-File-Formats\eFilingFormats\FEC_v8x\e-filing headers all versions.xlsx`

tabsheet `SA`

Compare with v8.4

2023-01-14

```{r}
scheduleAHeaders <-
  c("FORM_TYPE",
    "FILER_COMMITTEE_ID",
    "TRANSACTION_ID",
    "BACK_REFERENCE_TRAN_ID",
    "BACK_REFERENCE_SCHED_NAME",
    "ENTITY_TYPE",
    "CONTRIBUTOR_ORGANIZATION_NAME",
    "CONTRIBUTOR_LAST_NAME",
    "CONTRIBUTOR_FIRST_NAME",
    "CONTRIBUTOR_MIDDLE_NAME",
    "CONTRIBUTOR_PREFIX",
    "CONTRIBUTOR_SUFFIX",
    "CONTRIBUTOR_STREET_1",
    "CONTRIBUTOR_STREET_2",
    "CONTRIBUTOR_CITY",
    "CONTRIBUTOR_STATE",
    "CONTRIBUTOR_ZIP",
    "ELECTION_CODE",
    "ELECTION_OTHER_DESCRIPTION",
    "CONTRIBUTION_DATE",
    "CONTRIBUTION_AMOUNT",
    "CONTRIBUTION_AGGREGATE",
    "CONTRIBUTION_PURPOSE",
    "CONTRIBUTOR_EMPLOYER",
    "CONTRIBUTOR_OCCUPATION",
    "DONOR_COMMITTEE_FEC_ID",
    "DONOR_COMMITTEE_NAME",
    "DONOR_CANDIDATE_FEC_ID",
    "DONOR_CANDIDATE_LAST_NAME",
    "DONOR_CANDIDATE_FIRST_NAME",
    "DONOR_CANDIDATE_MIDDLE_NAME",
    "DONOR_CANDIDATE_PREFIX",
    "DONOR_CANDIDATE_SUFFIX",
    "DONOR_CANDIDATE_OFFICE",
    "DONOR_CANDIDATE_STATE",
    "DONOR_CANDIDATE_DISTRICT",
    "CONDUIT_NAME",
    "CONDUIT_STREET1",
    "CONDUIT_STREET2",
    "CONDUIT_CITY",
    "CONDUIT_STATE",
    "CONDUIT_ZIP",
    "MEMO_CODE",
    "MEMO_TEXT_DESCRIPTION",
    "Reference")
```

### SB Header

```{r}
scheduleBHeaders <-
  c("FORM_TYPE",
    "FILER_COMMITTEE_ID",
    "TRANSACTION_ID",
    "BACK_REFERENCE_TRAN_ID",
    "BACK_REFERENCE_SCHED_NAME",
    "ENTITY_TYPE",
    "PAYEE_ORGANIZATION_NAME",
    "PAYEE_LAST_NAME",
    "PAYEE_FIRST_NAME",
    "PAYEE_MIDDLE_NAME",
    "PAYEE_PREFIX",
    "PAYEE_SUFFIX",
    "PAYEE_STREET_1",
    "PAYEE_STREET_2",
    "PAYEE_CITY",
    "PAYEE_STATE",
    "PAYEE_ZIP",
    "ELECTION_CODE",
    "ELECTION_OTHER_DESCRIPTION",
    "EXPENDITURE_DATE",
    "EXPENDITURE_AMOUNT",
    "SEMI_ANNUAL_REFUNDED_BUNDLED_AMT",
    "EXPENDITURE_PURPOSE_DESCRIP",
    "CATEGORY_CODE",
    "BENEFICIARY_COMMITTEE_FEC_ID",
    "BENEFICIARY_COMMITTEE_NAME",
    "BENEFICIARY_CANDIDATE_FEC_ID",
    "BENEFICIARY_CANDIDATE_LAST_NAME",
    "BENEFICIARY_CANDIDATE_FIRST_NAME",
    "BENEFICIARY_CANDIDATE_MIDDLE_NAME",
    "BENEFICIARY_CANDIDATE_PREFIX",
    "BENEFICIARY_CANDIDATE_SUFFIX",
    "BENEFICIARY_CANDIDATE_OFFICE",
    "BENEFICIARY_CANDIDATE_STATE",
    "BENEFICIARY_CANDIDATE_DISTRICT",
    "CONDUIT_NAME",
    "CONDUIT_STREET_1",
    "CONDUIT_STREET_2",
    "CONDUIT_CITY",
    "CONDUIT_STATE",
    "CONDUIT_ZIP",
    "MEMO_CODE",
    "MEMO_TEXT_DESCRIPTION",
    "Reference")
```

### TEXT headers

```{r}
textHeaders <-
  c("REC_TYPE",
   "FILER_COMMITTEE_ID_NUMBER",
   "TRANSACTION_ID_NUMBER",
   "BACK_REFERENCE_TRAN_ID_NUMBER",
   "BACK_REFERENCE_SCHED_FORM_NAME",
   "TEXT4000")
```

## Packages

```{r}
library(tidyverse)

library(readxl)     # read_xlsx
library(writexl)    # write_xlsx

library(lubridate)

library(kableExtra)
library(ggplot2)
```

## Helper function

```{r}
Show <- function(data, caption = "", bigMark = "", ...)
{
  data                                            %>%
  kable("html", caption = caption,
        format.args = list(big.mark = bigMark))   %>%
  kable_styling(bootstrap_options = c("striped", "bordered", "condensed"),
                position = "left",
                full_width = FALSE, ...)
}
```

# Daily FEC filings

Source of daily FEC electronic files.

```{r}
baseDir <- "Z:/$/FEC-Electronic/"
```

Filter for files tagged with specified tag

```{r}
fecList <-
  read_xlsx(paste0(FEC_FILE_DIR, "FEC-Files.xlsx"))  %>%
  filter(Tag == TAG)                                 %>%                   #####
  arrange(`Coverage Start Date`)

fecList %>% Show()
```

Electronic filing dates are often a day after the reported `Filed Date` above. So, let's search for .fec file directory.

Let's verify these FEC files are available locally.

```{r}
fecFiles <-
  fecList           %>%
  mutate(
          pathName  = paste0(baseDir,
                             str_sub(`Filed Date`, 1, 4),
                             "/"),
          fileName  = paste0(str_replace(`FEC ID`, "FEC-", ""),
                             ".fec"),
          fullName  = "",
          sizeBytes = 0
        )
```

Most files are quite large

```{r}
for (i in 1:nrow(fecFiles))
{
  cat(i, fecFiles$pathName[i], fecFiles$fileName[i], "\n")
  fecFiles$fullName[i] <-
    list.files(path = fecFiles$pathName[i],
               pattern = paste0("*", fecFiles$fileName[i]),
               full.name = TRUE)  %>%  tail(1)  # latest date if more than 1
  fecFiles$sizeBytes[i] <- file.info(fecFiles$fullName[i])$size[1]
}

fecFiles %>%
  select(-pathName)                                       %>%
  mutate(fullName = str_sub(fullName, nchar(baseDir)+1))  %>%  # avoid html
  Show(bigMark = ",")
```

```{r}
stopifnot( all( file.exists(fecFiles$fullName) ) )
```

# Summarize records for each file

```{r}
fecFiles <-
  fecFiles  %>%
  mutate(Lines        = 0,
         SA11AI       = 0,
         ActBlue      = 0,
         Earmark      = 0,
         SA16         = 0,
         SB21B        = 0,
         SB23         = 0,
         SB28A        = 0,
         SB29         = 0,
         Contributors = 0,
         Recipients   = 0,
         Employers    = 0,
         FECVersion   = "") %>%
  relocate(FECVersion)
```


Process all current filings in batch (usually an election cycle)

```{r}
if (!dir.exists(Summary_DIR))
{
  dir.create(Summary_DIR, recursive = TRUE)
}
```

```{r}
options(width = 120)
for (i in 1:nrow(fecFiles))
{
  filename <- fecFiles$fullName[i]
  FILE_PREFIX <- paste0(Summary_DIR,
                        "FEC-", gsub(".fec", "", basename(filename)))

  d <- read_lines(filename)
  fecFiles$Lines[i] <- length(d)

  SEP = substr(d[1],4,4)

  fecFiles$FECVersion[i] <-
    paste(word(d[1], 2, 2, sep = SEP),
          word(d[1], 3, 3, sep = SEP))

  committeeNumber <- word(d[2], 2, 2, sep = SEP)
  committeeName   <- gsub(" ", "-", word(d[2], 3, 3, sep = SEP))
  filing          <- fecFiles$fullName[i]
  cat("\n----------\n",
      length(d), committeeName, committeeNumber, filing, "\n")
  cat(d[1], "\n")

  # formType <- word(d, 1,1, sep = fixed(SEP))                # VERY memory inefficient
  # formType <- unlist( sapply(strsplit(d, SEP), "[", 1) )    # slow
  # formType <- substr(d, 1, 8)                               # not good enough but fast
  formType <-substr(d, 1, regexpr(SEP,d) - 1)                 # good enough

  recordCounts <- table(formType, useNA = "ifany")
  print(recordCounts)

  fecFiles$SA11AI[i] <- recordCounts["SA11AI"]
  fecFiles$SA16[i]   <- recordCounts["SA16"]
  fecFiles$SB21B[i]  <- recordCounts["SB21B"]
  fecFiles$SB23[i]   <- recordCounts["SB23"]
  fecFiles$SB28A[i]  <- recordCounts["SB28A"]
  fecFiles$SB29[i]   <- recordCounts["SB29"]

  # SA11AI - Individuals, Itemized receipts
  dSubset <- d[formType == "SA11AI"]

  TEMPFILE <- "TempFile.txt"   # KLUDGE FOR NOW
  write_lines(dSubset, TEMPFILE)
  nLines <- length(dSubset)
  remove(dSubset)

  SA11AI <-
    read_delim(TEMPFILE,
               col_names = FALSE,
               delim = SEP,
               quote = "",
               col_types = cols(.default = "c"),
               guess_max = nLines)

  print( dim(SA11AI) )

  file.remove(TEMPFILE)

  names(SA11AI) <- scheduleAHeaders

  print(table(SA11AI$ENTITY_TYPE, useNA = "ifany"))

  purposeCounts <- table(SA11AI$CONTRIBUTION_PURPOSE, useNA = "ifany")
  print(table(SA11AI$CONTRIBUTION_PURPOSE, useNA = "ifany"))

  fecFiles$ActBlue[i] <- purposeCounts["Contribution to Act Blue"]
  fecFiles$Earmark[i] <- purposeCounts["Earmark"]

  # Raw Data

  SA11AI <-
    SA11AI  %>%
    select(-FORM_TYPE,                 # Try to save some memory
           -FILER_COMMITTEE_ID,
           -CONTRIBUTION_AGGREGATE,
           -starts_with("DONOR_C"),
           -starts_with("CONDUIT_"),
           -Reference)                                             %>%
    mutate(Source = basename(fecFiles$fullName[i]),
           CONTRIBUTION_AMOUNT = as.numeric(CONTRIBUTION_AMOUNT),
           CONTRIBUTION_PURPOSE  = ifelse(is.na(CONTRIBUTION_PURPOSE ), "-missing-", CONTRIBUTION_PURPOSE),
           MEMO_TEXT_DESCRIPTION = ifelse(is.na(CONTRIBUTION_PURPOSE ), "-missing-", MEMO_TEXT_DESCRIPTION),
           CONTRIBUTOR_EMPLOYER  = ifelse(is.na(CONTRIBUTOR_EMPLOYER ), "-missing-", CONTRIBUTOR_EMPLOYER)
          )

  print( nrow(SA11AI) )
  write_delim(SA11AI, paste0(FILE_PREFIX, "-", ORG, "-SA11AI-Contribution-Details.txt"),
              delim = SEP, escape = "none") # Too large for Excel in general

  # Summary by Contributor

  contributors <-
    SA11AI                       %>%
    group_by(CONTRIBUTOR_LAST_NAME,
             CONTRIBUTOR_FIRST_NAME,
             CONTRIBUTOR_MIDDLE_NAME,
             CONTRIBUTOR_PREFIX,
             CONTRIBUTOR_SUFFIX,
             CONTRIBUTOR_STREET_1,
             CONTRIBUTOR_STREET_2,
             CONTRIBUTOR_CITY,
             CONTRIBUTOR_STATE,
             CONTRIBUTOR_ZIP)    %>%
    summarize(nRecord            = n(),
              minContribution    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              maxContribution    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              medianContribution = median(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              Total              = sum(CONTRIBUTION_AMOUNT),
              Occupation         = str_flatten(sort(unique(CONTRIBUTOR_OCCUPATION)), collapse = "|"),
              Employer           = str_flatten(sort(unique(CONTRIBUTOR_EMPLOYER)),   collapse = "|"),
              Start              = min(CONTRIBUTION_DATE, na.rm = TRUE),
              End                = max(CONTRIBUTION_DATE, na.rm = TRUE),
              nRecipient         = n_distinct(MEMO_TEXT_DESCRIPTION),
              .groups = "drop"
             )                   %>%
    ungroup()                    %>%
    mutate(
            Days   = as.numeric( ymd(End) - ymd(Start) + 1 ),
            PerDay = round(nRecord / Days, 2)
          )                      %>%
    select(nRecord,
           min    = minContribution,
           max    = maxContribution,
           median = medianContribution,
           Total,
           Start, End,
           Days, PerDay,
           nRecipient,
           everything())         %>%
    arrange(-nRecord)

  print(nrow(contributors))
  fecFiles$Contributors[i] <- nrow(contributors)

  write_delim(contributors, paste0(FILE_PREFIX, "-", ORG, "-SA11AI-Contributors.txt"),
              delim = SEP, escape = "none")

  remove(contributors)

  # Summary by Recipient

  overallTotals <-
    SA11AI                        %>%
    summarize(nRecord             = n(),
               nRecipient         = n_distinct(MEMO_TEXT_DESCRIPTION),
               minContribution    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
               maxContribution    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
               medianContribution = median(CONTRIBUTION_AMOUNT, na.rm = TRUE),
               Total              = sum(CONTRIBUTION_AMOUNT),
               nOccupation        = n_distinct(CONTRIBUTOR_OCCUPATION),
               nEmployer          = n_distinct(CONTRIBUTOR_EMPLOYER),
               Start              = min(CONTRIBUTION_DATE, na.rm = TRUE),
               End                = max(CONTRIBUTION_DATE, na.rm = TRUE),
              )

  overallTotals %>%
    Show(bigMark = ",")

  # Recipients
  recipients <-
    SA11AI  %>%
    group_by(CONTRIBUTION_PURPOSE, MEMO_TEXT_DESCRIPTION)  %>%
    summarize(nRecord            = n(),
              minContribution    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              maxContribution    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              medianContribution = median(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              Total              = sum(CONTRIBUTION_AMOUNT),
              nOccupation        = n_distinct(CONTRIBUTOR_OCCUPATION),
              nEmployer          = n_distinct(CONTRIBUTOR_EMPLOYER),
              Start              = min(CONTRIBUTION_DATE, na.rm = TRUE),
              End                = max(CONTRIBUTION_DATE, na.rm = TRUE),
              .groups = "drop"
             )                   %>%
    ungroup()                    %>%
    mutate(
           Days   = as.numeric( ymd(End) - ymd(Start) + 1 ),
           PerDay = round(nRecord / Days, 2)
          )                          %>%
    select(nRecord,
           min    = minContribution,
           max    = maxContribution,
           median = medianContribution,
           Total,
           nOccupation, nEmployer,
           Start, End,
           Days, PerDay,
           CONTRIBUTION_PURPOSE, MEMO_TEXT_DESCRIPTION)   %>%
    arrange(CONTRIBUTION_PURPOSE, MEMO_TEXT_DESCRIPTION)

  print( nrow(recipients) )
  fecFiles$Recipients[i] <- nrow(recipients)

  recipients <-
    bind_rows(recipients,
              bind_cols(nRecord      = overallTotals$nRecord,
                        min          = overallTotals$minContribution,
                        max          = overallTotals$maxContribution,
                        median       = overallTotals$medianContribution,
                        Total        = overallTotals$Total,
                        nOccupation  = overallTotals$nOccupation,
                        nEmployer    = overallTotals$nEmployer,
                        Start        = overallTotals$Start,
                        End          = overallTotals$End,
                        Days         = as.numeric( ymd(overallTotals$End) -
                                                   ymd(overallTotals$Start) + 1 ),
                        PerDay       = round(overallTotals$nRecord /
                                             as.numeric( ymd(overallTotals$End) -
                                                   ymd(overallTotals$Start) + 1 ),
                                             2),
                        MEMO_TEXT_DESCRIPTION = "TOTAL / Overall")) %>%
    arrange(-nRecord)

  write_xlsx(recipients, paste0(FILE_PREFIX, "-", ORG, "-SA11AI-Recipients.xlsx"))
  remove(recipients)

  # Standardization

  employers <-
    SA11AI                          %>%
    mutate(CONTRIBUTOR_EMPLOYER =
             recode(CONTRIBUTOR_EMPLOYER,
                     "NOT EMPLOYED"       = "*NOT EMPLOYED",
                     "UNEMPLOYED"         = "*NOT EMPLOYED",
                     "NOT-EMPLOYED"       = "*NOT EMPLOYED",
                     "NONE"               = "*NOT EMPLOYED",
                     "NONENONE"           = "*NOT EMPLOYED",

                     "RETIRED"            = "*RETIRED",
                     "RET"                = "*RETIRED",
                     "RETIRED TEACHER"    = "*RETIRED",

                     "SELF EMPLOYED"      = "*SELF EMPLOYED",
                     "SELF-EMPLOYED"      = "*SELF EMPLOYED",

                     "MYSELF"             = "*SELF",
                     "SELF"               = "*SELF",

                     "N/A"                = "-missing-",

                     "FEDERAL GOVERNMENT" = "*US GOVERNMENT",
                     "US GOVERNMENT"      = "*US GOVERNMENT",
                     "US GOVT"            = "*US GOVERNMENT",

                     "USPS"               = "*US POSTAL SERVICE",
                     "US POSTAL SERVICE"  = "*US POSTAL SERVICE",

                     "HOME DEPOT"                = "*HOME DEPOT",
                     "HOME-DEPOT"                = "*HOME DEPOT",
                     "THE HOME DEPOT"            = "*HOME DEPOT",
                     "THE HOME DEPOT USA"        = "*HOME DEPOT",
                     "HOME DEPOT (CORPORATE HQ)" = "*HOME DEPOT",
                     "HOME DEPOT PRO"            = "*HOME DEPOT"
                   ),

           CONTRIBUTOR_OCCUPATION =
            recode(CONTRIBUTOR_OCCUPATION,
                     "N/A"                = "-missing-"
                  )
          )                         %>%

    # Employer Summary

    group_by(CONTRIBUTOR_EMPLOYER)  %>%
    summarize(nRecord            = n(),
              minContribution    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              maxContribution    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              medianContribution = median(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              Total              = sum(CONTRIBUTION_AMOUNT),
              nOccupation        = n_distinct(CONTRIBUTOR_OCCUPATION),
              Start              = min(CONTRIBUTION_DATE, na.rm = TRUE),
              End                = max(CONTRIBUTION_DATE, na.rm = TRUE),
              .groups = "drop"
             )                       %>%
    ungroup()                        %>%
    mutate(
           Days   = as.numeric( ymd(End) - ymd(Start) + 1 ),
           PerDay = round(nRecord / Days, 2)
          )                          %>%
    select(CONTRIBUTOR_EMPLOYER,
           nRecord,
           min    = minContribution,
           max    = maxContribution,
           median = medianContribution,
           Total,
           nOccupation,
           Start, End,
           Days, PerDay)   %>%
    arrange(-nRecord)

  print( nrow(employers) )
  fecFiles$Employers[i] <- nrow(employers)

  write_xlsx(employers, paste0(FILE_PREFIX, "-", ORG, "-SA11AI-Employers.xlsx"))
  remove(employers)

  remove(SA11AI)

  # Disbursements

  ## Itemized Disbursements
  disbursementsFields <- paste(scheduleBHeaders,collapse = SEP)

  dDisbursements <- d[formType == "SB21B"]
  if (length(dDisbursements) > 0)
  {
    write_lines(c(disbursementsFields, dDisbursements),
                paste0(FILE_PREFIX, "-", ORG, "-SB21B-Itemized-Disbursements.txt"))
  }

  ## Political Contributions
  dPolitical <- d[formType == "SB23"]
  if (length(dPolitical) > 0)
  {
    write_lines(c(disbursementsFields, dPolitical),
                paste0(FILE_PREFIX, "-", ORG, "-SB23-Political-Contributions.txt"))
  }

  ## Other Disbursements
  dOther <- d[formType == "SB29"]
  if (length(dOther) > 0)
  {
    write_lines(c(disbursementsFields, dOther),
                paste0(FILE_PREFIX, "-", ORG, "-SB29-Other-Disbursements.txt"))
  }

  # TEXT records
  dText <- d[formType == "TEXT"]
  if (length(dText) > 0)
  {
    write_lines(c(paste(textHeaders, collapse = SEP),
                  dText),
                paste0(FILE_PREFIX, "-", ORG, "-TEXT.txt"))
   }

  remove(d, formType, dText, dDisbursements, dPolitical, dOther)
}
```

```{r}
write_xlsx(fecFiles,
           paste0(TARGET_DIR, "Target-Files-", TAG, ".xlsx"))
```

# Fini {.tabset .tabset-fade .tabset-pills}

## {.active}

## Session Info

```{r epilogSessionInfo}
devtools::session_info()
```

</div>

```{r, echo=FALSE}
time.2 <- Sys.time()
processingTime <- paste("Processing time:",
                        sprintf("%.1f",
                                as.numeric(difftime(time.2, time.1,
                                                    units="secs"))), "secs\n")
```

`r processingTime`

`r format(Sys.time(), "%Y-%m-%d %H:%M")`
