---
output:
  html_document:
    code_download: true
    theme: cerulean
    toc: yes
    toc_depth:  3
    toc_float:
      collapsed:  yes
      smooth_scroll: yes
    number_sections: yes
    code_folding:  show
params:
    ORG: "ActBlue"
    TAG: "2022"

title : "`r paste('Explore Contribution Records:', ORG, 'in', TAG, 'Election Cycle')`"
author: "Earl F Glynn<br><small>watchdoglab.substack.com</small>"
date  : "<small>`r Sys.Date()`</small>"
---

```{r setup, echo = FALSE}
# http://biostat.mc.vanderbilt.edu/wiki/Main/KnitrHtmlTemplate
require(Hmisc)    # provides knitrSet and other functions
knitrSet(lang = 'markdown',   # If using blogdown: knitrSet(lang='blogdown')
         fig.align = 'left',
         w = 6.5,
         h = 4.5,
         cache = FALSE)
```

`r hidingTOC(buttonLabel = "Outline")`

```{r setup2, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment    = NA)

time.1 <- Sys.time()
```

# Setup {.tabset .tabset-fade .tabset-pills}

##  {.active}

## Constants

```{r}
EXCEL_LIMIT <- 2^20
```

```{r}
ORG <- params$ORG
TAG <- params$TAG
```

```{r}
TARGET_DIR  <- paste0("K:/Data-Farm/", ORG, "/", TAG, "/")
SUMMARY_DIR <- paste0(TARGET_DIR, "FEC-File-Summaries/")
```

```{r}
EXPLORE_DIR <- paste0(TARGET_DIR, "Explorations/")

if (!dir.exists(EXPLORE_DIR))
{
  dir.create(EXPLORE_DIR, recursive = TRUE)
}
```

## Packages

```{r}
library(tidyverse)

library(readxl)     # read_xlsx
library(writexl)    # write_xlsx

library(kableExtra)
library(ggplot2)

library(lubridate)  # ymd
```

## Helper function

```{r}
Show <- function(data, caption = "", bigMark = "", ...)
{
  data                                            %>%
  kable("html", caption = caption,
        format.args = list(big.mark = bigMark))   %>%
  kable_styling(bootstrap_options = c("striped", "bordered", "condensed"),
                position = "left",
                full_width = FALSE, ...)
}
```

# Contributor Summary

SA11AI:  FEC Form F3X, Schedule A, Line 11 [*Contributions (other than loans) From*], (a) "Individuals/Persons Other Than Political Committees", (i) Itemized

```{r}
readDetails <- function(filename)
{
  d <-
     read_delim(filename,
               delim = "\034",
               quote = "",
               col_types = cols(.default = "c"))

  d
}
```

```{r}
contributorDetail <- list.files(path    = SUMMARY_DIR,
                                pattern = "*-Contribution-Details.txt", full.names = TRUE)
length(contributorDetail)
```

```{r}
basename(contributorDetail)
```

```{r}
singleContributor <-
  contributorDetail  %>%
  map_df(readDetails)

dim(singleContributor)
```

```{r}
singleContributor <-
  singleContributor  %>%
  mutate(CONTRIBUTION_AMOUNT = as.numeric(CONTRIBUTION_AMOUNT),
         
         FullName = paste(CONTRIBUTOR_LAST_NAME, 
                          CONTRIBUTOR_FIRST_NAME, 
                          CONTRIBUTOR_MIDDLE_NAME,
                          CONTRIBUTOR_STREET_1,  
                          CONTRIBUTOR_CITY,
                          CONTRIBUTOR_STATE,
                          CONTRIBUTOR_ZIP,
                          sep = "|"),
         
         FullAddress = paste(CONTRIBUTOR_STREET_1, 
                             CONTRIBUTOR_STREET_2,  
                             CONTRIBUTOR_CITY,
                             CONTRIBUTOR_STATE,
                             CONTRIBUTOR_ZIP,
                             sep = "|"),
         
         CONTRIBUTOR_EMPLOYER   =
           recode(CONTRIBUTOR_EMPLOYER,
               "NOT EMPLOYED"           = "*NOT EMPLOYED",
               "UNEMPLOYED"             = "*NOT EMPLOYED",
               "NONE"                   = "*NOT EMPLOYED",
               "NONENONE"               = "*NOT EMPLOYED",
               "NONENOT EMPLOYED"       = "*NOT EMPLOYED",
               "NOT-EMPLOYED"           = "*NOT EMPLOYED",
               "NOT EMPLOYED NONE"      = "*NOT EMPLOYED",
               "NOT EMPLOYED NOW"       = "*NOT EMPLOYED",
               "CURRENTLY NOT EMPLOYED" = "*NOT EMPLOYED",
               
               "RETIRED"                 = "*RETIRED",
               "RET"                     = "*RETIRED",
               "RETIRED TEACHER"         = "*RETIRED",
               "NOT EMPLOYED/RETIRED"    = "*RETIRED",
               "NOT EMPLOYED-RETIRED"    = "*RETIRED",
               "NOT EMPLOYED - RETIRED"  = "*RETIRED",
               "NOT EMPLOYED  (RETIRED)" = "*RETIRED",
               "NOT EMPLOYED / RETIRED"  = "*RETIRED",
               "NOT EMPLOYEDRETIRED"     = "*RETIRED",
               "RETIRED - NOT EMPLOYED"  = "*RETIRED",
               "RETIRED NOT EMPLOYED"    = "*RETIRED",
               "RETIRED, NOT EMPLOYED"   = "*RETIRED",
              

               "SELF EMPLOYED"      = "*SELF EMPLOYED",
               "SELF-EMPLOYED"      = "*SELF EMPLOYED",
               "SELF- EMPLOYED"     = "*SELF EMPLOYED",
               "SELF EMPLOYEED"     = "*SELF EMPLOYED",
               "SELFEMPLOYED"       = "*SELF EMPLOYED",
               "SELF EMPLOY"        = "*SELF EMPLOYED",
               "SELF - EMPLOYED"    = "*SELF EMPLOYED",
               "MYSELF"             = "*SELF EMPLOYED",
               "SELF"               = "*SELF EMPLOYED",

               "N/A"                = "-missing-",

               "FEDERAL GOVERNMENT" = "*US GOVERNMENT",
               "US GOVERNMENT"      = "*US GOVERNMENT",
               "US GOVT"            = "*US GOVERNMENT",
               "FEDERAL GOVT"       = "*US GOVERNMENT",
               "FED GOVT"           = "*US GOVERNMENT",
               "U.S. GOVT"          = "*US GOVERNMENT",
               "US FEDERAL GOVT"    = "*US GOVERNMENT",
               "FED  GOVT"          = "*US GOVERNMENT",
               "U.S. GOVT."         = "*US GOVERNMENT",
               "U S GOVT"           = "*US GOVERNMENT",

               "USPS"                         = "*US POSTAL SERVICE",
               "US POSTAL SERVICE"            = "*US POSTAL SERVICE",
               "UNITED STATES POSTAL SERVICE" = "*US POSTAL SERVICE",
               "U.S. POSTAL SERVICE"          = "*US POSTAL SERVICE",
               "U S POSTAL SERVICE"           = "*US POSTAL SERVICE",
              
               "GOOGLE"             = "*GOOGLE",
               "GOOGLE, INC."       = "*GOOGLE",
               "GOOGLE LLC"         = "*GOOGLE",
               "GOOGLE INC."        = "*GOOGLE",
               "GOOGLE INC"         = "*GOOGLE",
               "GOOGLE, LLC"        = "*GOOGLE",
               "GOOGLE, INC"        = "*GOOGLE",
              
               "FACEBOOK"                 = "*FACEBOOK / META",
               "FACEBOOK, INC"            = "*FACEBOOK / META",
               "FACEBOOK, INC."           = "*FACEBOOK / META",
               "FACEBOOK INC"             = "*FACEBOOK / META",
               "FACEBOOK INC."            = "*FACEBOOK / META",
               "FACEBOOK. INC."           = "*FACEBOOK / META",
               "META PLATFORMS/FACEBOOK"  = "*FACEBOOK / META",
               "META"                     = "*FACEBOOK / META",
               "META INC"                 = "*FACEBOOK / META",
               "META PLATFORMS"           = "*FACEBOOK / META",
              
               "MICROSOFT"                = "*MICROSOFT",
               "MICROSOFT CORPORATION"    = "*MICROSOFT",
               "MICROSOFT CORP"           = "*MICROSOFT",
               "MICROSOFT CORP."          = "*MICROSOFT",
               "MICROSOFT, INC."          = "*MICROSOFT",
               "MICROSOFT, CORP."         = "*MICROSOFT",
              
               "TWITTER"                  = "*TWITTER",
               "TWITTER, INC."            = "*TWITTER",
               "TWITTER INC."             = "*TWITTER",
               "TWITTER, INC"             = "*TWITTER",
               "TWITTER INC"              = "*TWITTER",

               "HOME DEPOT"                   = "*HOME DEPOT",
               "HOME-DEPOT"                   = "*HOME DEPOT",
               "THE HOME DEPOT"               = "*HOME DEPOT",
               "THE HOME DEPOT USA"           = "*HOME DEPOT",
               "HOME DEPOT (CORPORATE HQ)"    = "*HOME DEPOT",
               "HOME DEPOT PRO"               = "*HOME DEPOT"
             ),

         CONTRIBUTOR_OCCUPATION =
          recode(CONTRIBUTOR_OCCUPATION,
                   "N/A"                = "-missing-"
                )
        )                        
```

```{r}
glimpse(singleContributor)
```

## Overall Counts

```{r}
OverallStats <-
  singleContributor  %>%
  summarize(
              n              = n(),
              
              totalAmount    = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              minAmount      = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              maxAmount      = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
              minDate        = min(CONTRIBUTION_DATE,   na.rm = TRUE),
              maxDate        = max(CONTRIBUTION_DATE,   na.rm = TRUE),

              nTranID        = n_distinct(TRANSACTION_ID),
              nBackTranID    = n_distinct(BACK_REFERENCE_TRAN_ID),
              nBackRef       = n_distinct(BACK_REFERENCE_SCHED_NAME),

              nOrgName       = n_distinct(CONTRIBUTOR_ORGANIZATION_NAME),
              nFullName      = n_distinct(FullName),
              nLastName      = n_distinct(CONTRIBUTOR_LAST_NAME),
              nFirstName     = n_distinct(CONTRIBUTOR_FIRST_NAME),
              nMiddleName    = n_distinct(CONTRIBUTOR_MIDDLE_NAME),
              nPrefix        = n_distinct(CONTRIBUTOR_PREFIX),
              nSuffix        = n_distinct(CONTRIBUTOR_SUFFIX),

              nStreet1       = n_distinct(CONTRIBUTOR_STREET_1),
              nStreet2       = n_distinct(CONTRIBUTOR_STREET_2),
              nCity          = n_distinct(CONTRIBUTOR_CITY),
              nState         = n_distinct(CONTRIBUTOR_STATE),
              nZip           = n_distinct(CONTRIBUTOR_ZIP),

              nElectionCode  = n_distinct(ELECTION_CODE),
              nElectionOther = n_distinct(ELECTION_OTHER_DESCRIPTION),

              nDate          = n_distinct(CONTRIBUTION_DATE),
              nAmount        = n_distinct(CONTRIBUTION_AMOUNT),
              nPurpose       = n_distinct(CONTRIBUTION_PURPOSE),
              nEmployers     = n_distinct(CONTRIBUTOR_EMPLOYER),
              nOccupations   = n_distinct(CONTRIBUTOR_OCCUPATION),

              nMemoCode      = n_distinct(MEMO_CODE),
              nEarmarks      = n_distinct(MEMO_TEXT_DESCRIPTION),  # Earmarks
              nSource        = n_distinct(Source)
           )

OverallStats %>% Show(bigMark = ",")
```

```{r}
write_xlsx(OverallStats, paste0(EXPLORE_DIR, ORG, "-", TAG, "-Overall-Counts.xlsx"))
```

## First few

```{r}
singleContributor %>% head(2) %>% Show()
```

## Last few

```{r}
singleContributor %>% tail(2) %>% Show()
```

# Fields

## TRANSACTION_ID

```{r}
c( min(singleContributor$TRANSACTION_ID), max(singleContributor$TRANSACTION_ID) )
```

field length

```{r}
table(nchar(singleContributor$TRANSACTION_ID))
```

Why two field lengths for `TRANSACTION_ID`?

## BACK_REFERENCE_TRAN_ID

```{r}
sum(is.na(singleContributor$BACK_REFERENCE_TRAN_ID))
```

## BACK_REFERENCE_SCHED_NAME

```{r}
sum(is.na(singleContributor$BACK_REFERENCE_SCHED_NAME))
```

## ENTITY_TYPE

```{r}
table(singleContributor$ENTITY_TYPE)
```

## CONTRIBUTOR_ORGANIZATION_NAME

```{r}
sum(is.na(singleContributor$CONTRIBUTOR_ORGANIZATION_NAME))
```

```{r}
orgs <-
  singleContributor                       %>%
  group_by(CONTRIBUTOR_ORGANIZATION_NAME) %>%
  count()                                 %>%
  ungroup()
```

```{r}
if (nrow(orgs) > 10)
{
  write_xlsx(orgs, paste0(EXPLORE_DIR, ORG, "-", TAG, "-Orgs.xlsx"))
} else {
  orgs %>% Show(bigMark = ",")
}
```

## CONTRIBUTOR_LAST_NAME

field length

```{r}
table(nchar(singleContributor$CONTRIBUTOR_LAST_NAME), useNA = "ifany")
```

```{r}
lastNames <-
  singleContributor               %>%
  group_by(CONTRIBUTOR_LAST_NAME) %>%
  summarize(nRecord      = n(),
            TotalAmount  = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate      = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate      = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            nEmployers   = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations = n_distinct(CONTRIBUTOR_OCCUPATION),  
            nEarmarks    = n_distinct(MEMO_TEXT_DESCRIPTION),
            .groups = "drop")     %>%
  ungroup()                       %>%
  arrange(-TotalAmount)

nrow(lastNames)
```

```{r}
lastNames %>% head(20) %>% Show()
```

Might be more than a million

```{r}
write_csv(lastNames,
          paste0(EXPLORE_DIR, ORG, "-", TAG, "-LastNames.csv"),
          quote = "all")
```

## CONTRIBUTOR_FIRST_NAME

field length

```{r}
table(nchar(singleContributor$CONTRIBUTOR_FIRST_NAME), useNA = "ifany")
```

```{r}
firstNames <-
  singleContributor                %>%
  group_by(CONTRIBUTOR_FIRST_NAME) %>%
  summarize(nRecord      = n(),
            TotalAmount  = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate      = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate      = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            nEmployers   = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations = n_distinct(CONTRIBUTOR_OCCUPATION),   
            nEarmarks    = n_distinct(MEMO_TEXT_DESCRIPTION),
            .groups = "drop")      %>%
  ungroup()                        %>%
  arrange(-TotalAmount)

nrow(firstNames)
```

```{r}
firstNames %>% head() %>% Show()
```

Might be more than a million

```{r}
write_csv(firstNames,
          paste0(EXPLORE_DIR, ORG, "-", TAG, "-FirstNames.csv"),
          quote = "all")
```

## CONTRIBUTOR_MIDDLE_NAME

field length

```{r}
table(nchar(singleContributor$CONTRIBUTOR_MIDDLE_NAME), useNA = "ifany")
```

```{r}
middleNames <-
  singleContributor                 %>%
  group_by(CONTRIBUTOR_MIDDLE_NAME) %>%
  summarize(nRecord     = n(),
            TotalAmount = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount   = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount   = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate     = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate     = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            nEmployers   = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations = n_distinct(CONTRIBUTOR_OCCUPATION),  
            nEarmarks   = n_distinct(MEMO_TEXT_DESCRIPTION),
            .groups = "drop")       %>%
  ungroup()                         %>%
  arrange(-TotalAmount)

nrow(middleNames)
```

```{r}
if (nrow(middleNames) > 2)
{
  write_csv(middleNames, paste0(EXPLORE_DIR, ORG, "-", TAG, "-MiddleNames.csv"))
} else {
  middleNames %>% Show()
}
```

## FullName

```{r}
FullName <-
  singleContributor     %>%
  group_by(FullName)    %>%
  summarize(nRecord     = n(),
            TotalAmount = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount   = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount   = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate     = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate     = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            Employer    = str_flatten(sort(unique(CONTRIBUTOR_EMPLOYER)),   collapse = "|"),
            Occupation  = str_flatten(sort(unique(CONTRIBUTOR_OCCUPATION)), collapse = "|"),
            nEarmarks   = n_distinct(MEMO_TEXT_DESCRIPTION),
            .groups = "drop")       %>%
  ungroup()                         

print( nrow(FullName) )
```

Might be more than a million

Sort descending by Total Amount

```{r}
write_csv(FullName %>% arrange(-TotalAmount), 
          paste0(EXPLORE_DIR, ORG, "-", TAG, "-FullNames-by-TotalAmount.csv"))
```

Sort descending by number of contributions

```{r}
write_csv(FullName %>% arrange(-nRecord), 
          paste0(EXPLORE_DIR, ORG, "-", TAG, "-FullNames-by-NumberOfContributions.csv"))
```

## FullAddress

```{r}
FullAddress <-
  singleContributor      %>%
  group_by(FullAddress)  %>%
  summarize(nRecord      = n(),
            TotalAmount  = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate      = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate      = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            nFullName    = n_distinct(FullName),
            nEmployers   = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations = n_distinct(CONTRIBUTOR_OCCUPATION),   
            nEarmarks    = n_distinct(MEMO_TEXT_DESCRIPTION),
            .groups      = "drop"
           )             %>%
  ungroup()              %>%
  arrange(-TotalAmount)

nrow(FullAddress)
```

Might be more than a million

```{r}
write_csv(FullAddress, paste0(EXPLORE_DIR, ORG, "-", TAG, "-FullAddress.csv"))
```
                                                                             
## CONTRIBUTOR_PREFIX

```{r}
sum(is.na(singleContributor$CONTRIBUTOR_PREFIX))
```

## CONTRIBUTOR_SUFFIX

```{r}
sum(is.na(singleContributor$CONTRIBUTOR_SUFFIX))
```

## CONTRIBUTOR_STREET_1

field length

```{r}
table(nchar(singleContributor$CONTRIBUTOR_STREET_1), useNA = "ifany")
```

```{r}
sum(is.na(singleContributor$CONTRIBUTOR_STREET_1))
```

```{r}
street1 <-
  singleContributor              %>%
  group_by(CONTRIBUTOR_STREET_1) %>%
  summarize(nRecord      = n(),
            TotalAmount  = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate      = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate      = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            nName        = n_distinct(FullName),
            nEmployers   = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations = n_distinct(CONTRIBUTOR_OCCUPATION),    
            nEarmarks    = n_distinct(MEMO_TEXT_DESCRIPTION),
            .groups = "drop"   
           )                     %>%
  ungroup()                      %>%
  arrange(-TotalAmount)

nrow(street1)
```

```{r}
street1 %>% head() %>% Show()
```


Might be more than a million?

```{r}
write_csv(street1,
          paste0(EXPLORE_DIR, ORG, "-", TAG, "-Street1.csv"),
          quote = "all")
```

## CONTRIBUTOR_STREET_2

```{r}
sum(is.na(singleContributor$CONTRIBUTOR_STREET_2))
```

```{r}
sum(is.na(singleContributor$CONTRIBUTOR_STREET_2))
```

## CONTRIBUTOR_CITY

## CONTRIBUTOR_STATE

```{r}
table(singleContributor$CONTRIBUTOR_STATE, useNA = "ifany")
```

## CONTRIBUTOR_ZIP

5-digit, 9-digit ZIPs; foreign postal codes

```{r}
table(nchar(singleContributor$CONTRIBUTOR_ZIP), useNA = "ifany")
```

```{r}
zipLengthByState <-
  singleContributor                             %>%
  mutate(zipLength = nchar(CONTRIBUTOR_ZIP))    %>%
  group_by(CONTRIBUTOR_STATE, zipLength)        %>%
  count()                                       %>%
  ungroup()                                     %>%
  spread(zipLength, n, fill = 0)                %>%
  arrange(CONTRIBUTOR_STATE)
```

```{r}
write_xlsx(zipLengthByState,
           paste0(EXPLORE_DIR, ORG, "-", TAG, "-ZipLengthByState.xlsx"))
```

## ELECTION_CODE

```{r}
sum(!is.na(singleContributor$ELECTION_CODE))
```

```{r}
singleContributor      %>%
  count(ELECTION_CODE) %>%
  Show(bigMark = ",")
```

```{r}
electionCodes <-
  singleContributor           %>%
    filter(!is.na(singleContributor$ELECTION_CODE))

write_xlsx(head(electionCodes, 1000),
           paste0(EXPLORE_DIR, ORG, "-", TAG, "-Election-Codes.xlsx"))
```

## ELECTION_OTHER_DESCRIPTION

```{r}
sum(is.na(singleContributor$ELECTION_OTHER_DESCRIPTION))
```

## CONTRIBUTION_DATE and CONTRIBUTION_AMOUNT

```{r}
c( min(singleContributor$CONTRIBUTION_DATE), max(singleContributor$CONTRIBUTION_DATE) )
```

```{r}
monthCounts <-
  singleContributor  %>%
  mutate(yyyy = str_sub(CONTRIBUTION_DATE, 1, 4),
         mm   = str_sub(CONTRIBUTION_DATE, 5, 6))    %>%
  group_by(yyyy, mm)  %>%
  summarize(n = n(), .groups = "drop")  %>%
  ungroup()           %>%
  spread(mm, n)

monthCounts %>%
  Show(bigMark = ",")
```

```{r}
monthAmounts <-
  singleContributor  %>%
  mutate(yyyy = str_sub(CONTRIBUTION_DATE, 1, 4),
         mm   = str_sub(CONTRIBUTION_DATE, 5, 6))    %>%
  group_by(yyyy, mm)  %>%
  summarize(totalAmount =sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            .groups = "drop")  %>%
  ungroup()   %>%
  spread(mm, totalAmount)

monthAmounts %>% Show(bigMark = ",")
```

```{r}
dayAmounts <-
  singleContributor  %>%
  group_by(CONTRIBUTION_DATE)  %>%
  summarize(nRecord     = n(),
            totalAmount = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            nName       = n_distinct(FullName),
            nEmployers   = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations = n_distinct(CONTRIBUTOR_OCCUPATION),
            nEarmarks    = n_distinct(MEMO_TEXT_DESCRIPTION),       
            .groups = "drop")  %>%
  ungroup()                    %>%
  arrange(CONTRIBUTION_DATE)

nrow(dayAmounts)
```

```{r}
dayAmounts %>% head() %>% Show()
```

```{r}
write_xlsx(dayAmounts,
           paste0(EXPLORE_DIR, ORG, "-", TAG, "-Contributions-by-Day.xlsx"))
```

```{r}
sum(is.na(singleContributor$CONTRIBUTION_DATE))
```

```{r}
sum(is.na(singleContributor$CONTRIBUTION_AMOUNT))
```

## CONTRIBUTION_PURPOSE

```{r}
sum(is.na(singleContributor$CONTRIBUTION_PURPOSE))
```

```{r}
table(singleContributor$CONTRIBUTION_PURPOSE,
      singleContributor$ENTITY_TYPE)
```


```{r}
purposeCounts <-
  singleContributor              %>%
  group_by(ENTITY_TYPE,
           CONTRIBUTION_PURPOSE) %>%
  summarize(nRecord      = n(),
            TotalAmount  = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate      = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate      = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            nName        = n_distinct(FullName),
            nEmployers   = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations = n_distinct(CONTRIBUTOR_OCCUPATION), 
            nEarmarks    = n_distinct(MEMO_TEXT_DESCRIPTION),
            .groups = "drop")  %>%
  ungroup()

purposeCounts %>%
  Show(bigMark = ",")

write_xlsx(purposeCounts,
           paste0(EXPLORE_DIR, ORG, "-", TAG, "-Purpose-Counts.xlsx"))
```

## CONTRIBUTOR_EMPLOYER

```{r}
sum(is.na(singleContributor$CONTRIBUTOR_EMPLOYER))
```

```{r}
employerStats <-
  singleContributor              %>%
  
  group_by(CONTRIBUTOR_EMPLOYER) %>%
  summarize(nRecord = n(),
            TotalAmount  = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate      = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate      = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            nName        = n_distinct(FullName),
            nOccupations = n_distinct(CONTRIBUTOR_OCCUPATION),
            nEarmarks    = n_distinct(MEMO_TEXT_DESCRIPTION),
            nState       = n_distinct(CONTRIBUTOR_STATE),
            nSource      = n_distinct(Source),
            .groups = "drop")    %>%
  ungroup()                      %>%
  arrange(-TotalAmount)

nrow(employerStats)
```

```{r}
employerStats %>% head(5) %>% Show()
```

```{r}
write_csv(employerStats,
          paste0(EXPLORE_DIR, ORG, "-", TAG, "-Employer-Stats.csv"),
          quote = "all")
```

```{r}
table(employerStats$nName)
```

```{r}
table(employerStats$nState)
```

## CONTRIBUTOR_OCCUPATION

```{r}
sum(is.na(singleContributor$CONTRIBUTOR_OCCUPATION))
```

````{r}
occupationStats <-
  singleContributor                %>%
  group_by(CONTRIBUTOR_OCCUPATION) %>%
  summarize(nRecord = n(),
            TotalAmount  = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount    = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount    = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate      = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate      = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            nName        = n_distinct(FullName),
            nEmployers   = n_distinct(CONTRIBUTOR_EMPLOYER),   
            nEarmarks    = n_distinct(MEMO_TEXT_DESCRIPTION),
            .groups = "drop")    %>%
  ungroup()                      %>%
  arrange(-TotalAmount)

nrow(occupationStats)
```

```{r}
occupationStats %>% head(5) %>% Show()
```

```{r}
write_csv(occupationStats,
          paste0(EXPLORE_DIR, ORG, "-", TAG, "-Occupation-Stats.csv"),
          quote = "all")
```

## MEMO_CODE

```{r}
sum(is.na(singleContributor$MEMO_CODE))
```

## MEMO_TEXT_DESCRIPTION:  Earmarks

```{r}
overallTotals <-
  singleContributor                            %>%
  summarize(nFECFilings        = n_distinct(Source),

            nRecord            = n(),
            TotalAmount        = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount          = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount          = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minDate            = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate            = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            
            nName              = n_distinct(FullName),
            nEmployers         = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations       = n_distinct(CONTRIBUTOR_OCCUPATION), 

            # These can be wrong when there are replacement .fec file(s)
            # not included in a daily FEC electronic .zip
            firstFECFiling     = min(Source, na.rm = TRUE),
            lastFECFiling      = max(Source, na.rm = TRUE)
           )                   %>%  
  
   mutate(
          Days   = as.numeric( ymd(maxDate) - ymd(minDate) + 1),
          PerDay = round(nRecord / Days, 2),
          CONTRIBUTION_PURPOSE  = NA,
          MEMO_TEXT_DESCRIPTION = "TOTAL",
          committee             = "",
        )                       %>%
  
  select(nFECFilings,

         nRecord,
         TotalAmount,
         nName,
         nEmployers,
         nOccupations,

         min    = minAmount,
         max    = maxAmount,

         start  = minDate,
         end    = maxDate,
         Days, 
         PerDay,
         CONTRIBUTION_PURPOSE,
         MEMO_TEXT_DESCRIPTION,
         committee,
         firstFECFiling, lastFECFiling)         
```

```{r}
earmarkSummary <-
  singleContributor                            %>%
  mutate(committee =
           MEMO_TEXT_DESCRIPTION               %>%  # should be an easier way
           stringi::stri_reverse()             %>%  # to extract committee
           str_extract("(?<=\\))(.*?)(?=\\()") %>%
           stringi::stri_reverse()
        )                      %>%                                  
  group_by(CONTRIBUTION_PURPOSE,
           MEMO_TEXT_DESCRIPTION,
           committee)          %>%
  summarize(nFECFilings        = n_distinct(Source),

            nRecord            = n(),
            
            TotalAmount        = sum(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            minAmount          = min(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            maxAmount          = max(CONTRIBUTION_AMOUNT, na.rm = TRUE),
            
            minDate            = min(CONTRIBUTION_DATE,   na.rm = TRUE),
            maxDate            = max(CONTRIBUTION_DATE,   na.rm = TRUE),
            
            nName              = n_distinct(FullName),
            nEmployers         = n_distinct(CONTRIBUTOR_EMPLOYER),
            nOccupations       = n_distinct(CONTRIBUTOR_OCCUPATION),        

            # These can be wrong when there are replacement .fec file(s)
            # not included in a daily FEC electronic .zip
            firstFECFiling     = min(Source, na.rm = TRUE),
            lastFECFiling      = max(Source, na.rm = TRUE),
            .groups = "drop"
           )                   %>%
  ungroup()                    %>%
  mutate(
          Days   = as.numeric( ymd(maxDate) - ymd(minDate) + 1),
          PerDay = round(TotalAmount / Days, 2)
        )                      %>%
  select(nFECFilings,

         nRecord,
         TotalAmount,
         
         nName,
         nEmployers,
         nOccupations,

         min    = minAmount,
         max    = maxAmount,

         start  = minDate,
         end    = maxDate,
         Days, 
         PerDay,
         everything())         
```                                              

```{r}
earmarkSummaryWithTotals <-
  bind_rows(overallTotals,
            earmarkSummary)  %>%
  arrange(-TotalAmount)

nrow(earmarkSummaryWithTotals)
```

```{r}
earmarkSummaryWithTotals %>% head(20) %>% Show()
```

```{r}
write_xlsx(earmarkSummaryWithTotals,
           paste0(EXPLORE_DIR, ORG, "-", TAG, "-Earmarks-Memo-Text.xlsx"))
```

## Source

```{r}
sum(is.na(singleContributor$Source))
```

```{r}
sourceCounts <-
  singleContributor      %>%
    count(Source)

nrow(sourceCounts)
```

```{r}
sourceCounts %>% Show(bigMark = ",")
```

```{r}
write_xlsx(sourceCounts,
           paste0(EXPLORE_DIR, ORG, "-", TAG, "-Source-Counts.xlsx"))
```

# Fini {.tabset .tabset-fade .tabset-pills}

## {.active}

## Session Info

```{r epilogSessionInfo}
devtools::session_info()
```

</div>

```{r, echo=FALSE}
time.2 <- Sys.time()
processingTime <- paste("Processing time:",
                        sprintf("%.1f",
                                as.numeric(difftime(time.2, time.1,
                                                    units="secs"))), "secs\n")
```

`r processingTime`

`r format(Sys.time(), "%Y-%m-%d %H:%M")`
